---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# efficientize



Efficientize writing and programming



## Functions


* `formalize_writing()` applies
  * `capitalize_sentences()` to
    * capitalize the first letter of the first word in each sentence
  * `capitalize_headings()` to
    * capitalize the first letter of the first word in rmd headings
  * `replace_based_on_dict()` to
    * replace shorthands with full spellings see https://github.com/xf15/efficientize/blob/main/data-raw/dict_writing.csv

You can supply the source file name only to change the source file directly, e.g., `formalize_writing("informal_paper.Rmd")` or in addition supply a destination file name to create a new file, e.g.,     

```
formalize_writing("informal_paper.Rmd", "formal_paper.Rmd")
```
see [informal_paper.Rmd](https://github.com/xf15/efficientize/tree/main/vignettes/informal_paper.Rmd)
see [formal_paper.Rmd](https://github.com/xf15/efficientize/tree/main/vignettes/formal_paper.Rmd)

* `update_psychopy_script_for_multiple_lists()` applies
  * `replace_based_on_dict()` to
    * modify psyexp script used for a single list to be used as script for task combining all lists see https://github.com/xf15/efficientize/blob/main/data-raw/dict_psyexp.csv


## Templates


```
usethis::use_rmarkdown_template(template_name = "scratch", template_description = "for exploration")
usethis::use_rmarkdown_template(template_name = "slides", template_description = "template for slides")
usethis::use_rmarkdown_template(template_name = "manuscript", template_description = "template for manuscript")

```
https://github.com/xf15/efficientize/blob/main/inst/rmarkdown/templates/default/skeleton/skeleton.Rmd

https://github.com/xf15/efficientize/blob/main/inst/rmarkdown/templates/slides/skeleton/skeleton.Rmd

https://github.com/xf15/efficientize/blob/main/inst/rmarkdown/templates/manuscript/skeleton/skeleton.Rmd



https://bookdown.org/yihui/rmarkdown/template-structure.html



## Installation

files in `/inst` with prefix my_ need to be synced to your own files 

so fork, clone

throughout this project, replace

```
/Users/xzfang/Github/efficientize/
```

with your repo path

```
devtools::install()
```

## update 
this pkg needs to be updated as your own files are updated 
first, update dict
updates in inst files will apply once pkg reinstalled 
```{r}
source('data-raw/create_dict.R')

devtools::install()
```


## Documentation

https://xf15.github.io/efficientize/

## todo

efficientize::update_psychopy_script_for_multiple_lists("/Users/xzfang/Github/ideal_adapter/interface_exp2.psyexp", "/Users/xzfang/Github/ideal_adapter/ideal_adapter_exp2_List_All/interface_exp2_list_all.psyexp")

only work when in project environment

go through all check warnings and note, rmd papers should be in inst/doc

why no https://github.com/xf15/efficientize/blob/main/R/data.R for psyexp


## note

copy first line of roxygen function comment for function here

the rest lines of roxygen comment should be copied from inline comments, replacing #' with # otherwise get all code recognized as roxygen get @export may only span a single line, supposed to be already fixed though https://github.com/r-lib/roxygen2/issues/737



str_locate_all gives named matrix, find dealt with as matrix searching nrow, rest dealt with as vector

substr

https://evoldyn.gitlab.io/evomics-2018/ref-sheets/R_strings.pdf
