---
output:
  github_document:
    toc: true
    toc_depth: 3
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# efficientize



Efficientize writing and programming

## what it does

### Functions

in writing_help.R

* `formalize_writing()` applies
  * `replace_based_on_dict()` to
    * replace shorthands with full spellings see https://github.com/xf15/efficientize/blob/main/data-raw/dict_writing.csv
  * `capitalize_sentences()` to
    * capitalize the first letter of the first word in each sentence
  * `capitalize_headings()` to
    * capitalize the first letter of the first word in rmd headings


You can supply the source file name only to change the source file directly, e.g., `formalize_writing("informal_paper.Rmd")` or in addition supply a destination file name to create a new file, e.g.,

```
formalize_writing("informal_paper.Rmd", "formal_paper.Rmd")
```
for a demo
see [informal_paper.Rmd](https://github.com/xf15/efficientize/tree/main/vignettes/informal_paper.Rmd)
see [formal_paper.Rmd](https://github.com/xf15/efficientize/tree/main/vignettes/formal_paper.Rmd)

in exp_repo.R

* `add_papers()`
  * export pdf of papers cited in manuscript from zotero to /relevant_papers of https://github.com/xf15/efficientize_exp_repo_template

here is how i use all of these functions
https://github.com/xf15/efficientize_exp_repo_template/blob/main/manuscript/render_manuscript.R



### Templates


```
usethis::use_rmarkdown_template(template_name = "scratch", template_description = "for exploration")
usethis::use_rmarkdown_template(template_name = "slides", template_description = "template for slides")
usethis::use_rmarkdown_template(template_name = "manuscript", template_description = "template for manuscript")

```
https://github.com/xf15/efficientize/blob/main/inst/rmarkdown/templates/scratch/skeleton/skeleton.Rmd

https://github.com/xf15/efficientize/blob/main/inst/rmarkdown/templates/slides/skeleton/skeleton.Rmd

https://github.com/xf15/efficientize/blob/main/inst/rmarkdown/templates/manuscript/skeleton/skeleton.Rmd



## how to use

### start

you want to define your own `dict` in `/data-raw`

you need to sync your own zotero bib to that in `/inst/files_for_efficientize_exp_repo_template`

you need to `ln` your own bash files to those in `/inst/files_for_unrelated_housekeeping`

so fork, clone

in your text editor, throughout this project, replace

```
/Users/xzfang/Github/efficientize/
```

with your repo path

```
devtools::install()
```

### update

as all those customized files mentioned above get updated, this pkg need to be reinstalled

do

```
(base) Xinzhus-MacBook-Pro:efficientize xzfang$ Rscript update.R
```

which

```
rmarkdown::render("README.Rmd")
```

which

```{r}
source('data-raw/create_dict.R')

devtools::install()
```
