---
title: "writing_help"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{writing_help}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(efficientize)
``` 

Call `formalize_writing()` which applies `capitalize_sentences()` to capitalize the first letter of the first word in each sentence and applies `capitalize_headings()` to capitalize the first letter of the first word in rmd headings. You can supply the source file name only to change the source file directly, e.g., `formalize_writing("informal_paper.Rmd")` or in addition supply a destination file name to create a new file, e.g., 
```{r} 
formalize_writing("informal_paper.Rmd", "formal_paper.Rmd")
```
see [informal_paper.Rmd](https://github.com/xf15/efficientize/tree/main/vignettes/informal_paper.Rmd)
see [formal_paper.Rmd](https://github.com/xf15/efficientize/tree/main/vignettes/formal_paper.Rmd)

